cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-11-28 paper-cardinalR.Rmd
Added branch parameters to the table

```{r}
branch_tb <- tibble(fun = c("gen_expbranches",
                             "gen_linearbranches",
                             "gen_curvybranches", 
                             "gen_orglinearbranches", 
                             "gen_orgcurvybranches"), 
                      exp = c("Exponential shaped branches.",
                               "Linear shaped branches.", 
                               "Curvy shaped branches.",
                               "Linear shaped branches originated in one point.",
                               "Curvy shaped branches originated in one point.")) |> 
   mutate(fun = gsub("_", "\\\\_", fun))
```

```{r branching-tb-html, eval=knitr::is_html_output()}
branch_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR branching data generation functions", col.names = c("Function", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r branching-tb-pdf, eval=knitr::is_latex_output()}
branch_tb |>
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

```{r}
arg_branching_tb <- tibble(arg = c("n", "k"), 
                          type = c("integer", "integer"),
                        exp = c("Number of points.",
                                "Number of clusters."))
```

```{r arg-branching-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Type", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r arg-branching-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Type", "Explanation"), booktabs = T, escape = FALSE, table.pos = "!ht")  |>
  column_spec(1, width = "1cm") |>
  column_spec(1, width = "2cm") |>
  column_spec(2, width = "3cm")
```

@@

```{r data-linearbranches, echo=TRUE}
linearbranches <- gen_linearbranches(n = 1000, k = 4)
```

@@

```{r data-curvybranches, echo=TRUE}
curvybranches <- gen_curvybranches(n = 1000, k = 4)
```

@@

```{r data-expbranches, echo=TRUE}
expbranches <- gen_expbranches(n = 1000, k = 4)
```

@@

```{r data-orglinearbranches, echo=TRUE}
orglinearbranches <- gen_orglinearbranches(n = 1000, p = 4, k = 4)
```

@@

```{r data-orgcurvybranches, echo=TRUE}
orgcurvybranches <- gen_orgcurvybranches(n = 1000, p = 4, k = 4)
```

>>>>

```{r}
branch_tb <- tibble(fun = c("gen_expbranches",
                             "gen_linearbranches",
                             "gen_curvybranches", 
                             "gen_orglinearbranches", 
                             "gen_orgcurvybranches"),
                    parm = c("n, k",
                             "n, k",
                             "n, k",
                             "n, p, k",
                             "n, p, k"),
                      exp = c("Exponential shaped branches.",
                               "Linear shaped branches.", 
                               "Curvy shaped branches.",
                               "Linear shaped branches originated in one point.",
                               "Curvy shaped branches originated in one point.")) |> 
   mutate(fun = gsub("_", "\\\\_", fun))
```

```{r branching-tb-html, eval=knitr::is_html_output()}
branch_tb |> 
  mutate(parm = paste0("<code>", parm, "</code>")) |>
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR branching data generation functions", col.names = c("Function", "Arguments", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r branching-tb-pdf, eval=knitr::is_latex_output()}
branch_tb |>
  mutate(parm = paste0("\\texttt{", parm, "}")) |>
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Arguments", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "3.5cm") |>
  column_spec(2, width = "1.5cm") |>
  column_spec(3, width = "8cm")
```

```{r}
arg_branching_tb <- tibble(arg = c("n", "k", "p"), 
                          type = c("integer", "integer", "integer"),
                        exp = c("Number of points.",
                                "Number of clusters.",
                                "Number of dimensions."))
```

```{r arg-branching-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  mutate(arg = paste0("<code>", arg, "</code>")) |>
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Type", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r arg-branching-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  mutate(arg = paste0("\\texttt{", arg, "}")) |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Type", "Explanation"), booktabs = T, escape = FALSE, table.pos = "!ht")  |>
  column_spec(1, width = "1cm") |>
  column_spec(1, width = "2cm") |>
  column_spec(2, width = "3cm")
```

@@

```{r data-linearbranches}
linearbranches <- gen_linearbranches(n = 1000, k = 4)
```

@@

```{r data-curvybranches}
curvybranches <- gen_curvybranches(n = 1000, k = 4)
```

@@

```{r data-expbranches}
expbranches <- gen_expbranches(n = 1000, k = 4)
```

@@

```{r data-orglinearbranches}
orglinearbranches <- gen_orglinearbranches(n = 1000, p = 4, k = 4)
```

@@

```{r data-orgcurvybranches}
orgcurvybranches <- gen_orgcurvybranches(n = 1000, p = 4, k = 4)
```

### 2025-11-28 paper-cardinalR.tex
Added branch parameters to the table

\caption{\label{tab:branching-tb-pdf}cardinalR branching data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
\texttt{gen\_expbranches} & Exponential shaped branches.\\
\texttt{gen\_linearbranches} & Linear shaped branches.\\
\texttt{gen\_curvybranches} & Curvy shaped branches.\\
\texttt{gen\_orglinearbranches} & Linear shaped branches originated in one point.\\
\texttt{gen\_orgcurvybranches} & Curvy shaped branches originated in one point.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:arg-branching-tb-pdf}The main arguments for branching shape generators.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{3cm}l}
\toprule
Argument & Type & Explanation\\
\midrule
n & integer & Number of points.\\
k & integer & Number of clusters.\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{verbatim}
linearbranches <- gen_linearbranches(n = 1000, k = 4)
\end{verbatim}

@@

\begin{verbatim}
curvybranches <- gen_curvybranches(n = 1000, k = 4)
\end{verbatim}

@@

\begin{verbatim}
expbranches <- gen_expbranches(n = 1000, k = 4)
\end{verbatim}

@@

\begin{verbatim}
orglinearbranches <- gen_orglinearbranches(n = 1000, p = 4, k = 4)
\end{verbatim}

\begin{verbatim}
orgcurvybranches <- gen_orgcurvybranches(n = 1000, p = 4, k = 4)
\end{verbatim}

>>>>

\caption{\label{tab:branching-tb-pdf}cardinalR branching data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Arguments & Explanation\\
\midrule
\texttt{gen\_expbranches} & \texttt{n, k} & Exponential shaped branches.\\
\texttt{gen\_linearbranches} & \texttt{n, k} & Linear shaped branches.\\
\texttt{gen\_curvybranches} & \texttt{n, k} & Curvy shaped branches.\\
\texttt{gen\_orglinearbranches} & \texttt{n, p, k} & Linear shaped branches originated in one point.\\
\texttt{gen\_orgcurvybranches} & \texttt{n, p, k} & Curvy shaped branches originated in one point.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:arg-branching-tb-pdf}The main arguments for branching shape generators.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{3cm}l}
\toprule
Argument & Type & Explanation\\
\midrule
\texttt{n} & integer & Number of points.\\
\texttt{k} & integer & Number of clusters.\\
\texttt{p} & integer & Number of dimensions.\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

@@

@@
